---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Numpute

<!-- badges: start -->
<!-- badges: end -->

The goal of CorrClust is to find groups (clusters) of correlated variables within a dataset.

## Installation

You can install the development version of Numpute from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("easoneli176/CorrClust")
```

## Example

First, the CorrTab function makes finding the correlations between numeric columns simple. Note that if a row value is missing in one vector, that row will be cut from the pairwise correlation calculation.

```{r example}
library(CorrClust)

mock_data <- data.frame(pred1 = rep(1:4,10),pred2=rep(1:5,8),missvar=as.numeric(c("NA",rep(1:2,19),"NA")))
CorrTab(mock_data)
```

The CorrClust function goes one step further and uses this table to cluster the columns into groups. The user can decide the threshold for how highly variables must be correlated to be grouped.

```{r example2}
CorrClust(mock_data,.4)
```

Finally, if for some reason you wish to use correlations calcualted differently than the base R package, you can use a table of correlation values as input in CorrClust2

```{r example3}
CorrClust2(CorrTab(mock_data),.4)
```
